\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\small{Updated April 15, 2024}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeAffiliationSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{flushleft}
    \textbf{\Huge \scshape Max Fierro} \\ \vspace{1pt}
    \href{mailto:maxfierro@berkeley.com}{\underline{maxfierro@berkeley.edu}} $|$ 
    \href{https://www.maxfierro.me}{\underline{www.maxfierro.me}} $|$ 
    \small (619) 496-1150
\end{flushleft}


%-----------EDUCATION-----------
\section{Academic History}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Aug. 2021 -- July 2025}
      {B.A. Computer Science, Minor in Mathematics; GPA: 3.51}{Berkeley, CA}


    \resumeSubSubheading{
      \textbf{Selected Coursework:}
      \textit{Operating Systems and Systems Programming},
      \textit{Introduction to Database Systems}, \\
      \textit{Computer Architecture},
      \textit{Efficient Algorithms and Intractable Problems},
      \textit{Discrete Mathematics and} \\
      \textit{Probability Theory}.
      }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern (ML Systems)}{May 2024 -- Aug. 2024}
      {Meta Platforms, Inc.}{Menlo Park, CA}
      \resumeItemListStart
        \resumeItem{Starting work with the Ads Training Data and Model Infrastructure group in Summer of 2024.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern (Ads Optimization)}{May 2023 -- Aug. 2023}
      {Meta Platforms, Inc.}{Menlo Park, CA}
      \resumeItemListStart
        \resumeItem{Work on a pre-alpha \textbf{advertiser value optimization} feature within the Ads Bidding team.}
        \resumeItem{Contribute to \textbf{data schema and system design} via comprehensive feasibility studies.}
        \resumeItem{Collaborate with product designers and market researchers to consolidate an \textbf{alpha specification.}}
        \resumeItem{Expand the \textbf{Meta Ads Manager} web interface to produce bid multiplier data to global ad delivery system.}
      \resumeItemListEnd

    \resumeSubheading
      {MetaU Engineering Intern (WhatsApp)}{June 2022 -- Aug. 2022}
      {Meta Platforms, Inc.}{Menlo Park, CA}
      \resumeItemListStart
        \resumeItem{Learned \textbf{large-scale application design} with the WhatsApp Data Archive and Transport team.}
        \resumeItem{Participated in a bootcamp-style course on Obj-C and Swift \textbf{iOS development} using UIKit and SwiftUI.}
        \resumeItem{Designed and implemented a \textbf{task management application} (see ``Process'') as a capstone project.}
    \resumeItemListEnd

    \resumeSubheading
      {Lead Endpoint Engineer}{May 2022 -- Feb. 2024}
      {UC Berkeley SAIT}{Berkeley, CA}
      \resumeItemListStart
        \resumeItem{Provide advising to \textbf{UC Berkeley IT leaders and CIO} as part of the Student Technology Council.}
        \resumeItem{\textbf{Lead} an endpoint management team responsible for the security and accessibility of more than 400 devices.}
        \resumeItem{Maintain campus partnerships and \textbf{oversee organizational work}, such as the hiring of 3 engineers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AFFILIATIONS-----------
\section{Current Affiliations}
    \resumeSubHeadingListStart
    \resumeAffiliationSubheading
    {\textbf{GamesCrafters} $|$ Prof. Dan Garcia's computational game theory applied research group.}{Jan. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{strong solution to Five-Field Kono}, a game of $>10^9$ positions (\href{https://nyc.cs.berkeley.edu/uni/games/fivefieldkono/variants/regular}{\underline{play against solution}}).}
            \resumeItem{\textbf{Re-architected C codebase} for ergonomics, safety, and multi-processing support (see ``GamesmanNova'').}
            \resumeItem{Designed an \textbf{LSM-Tree based database engine} for enabling parallelization in game solves while optimizing for game-theoretic algorithms' access patterns.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{GamesmanNova} $|$ Abstract strategy game analysis system.}
          \resumeItemListStart
            \resumeItem{System for performing \textbf{full game tree exploration} on deterministic abstract strategy finite-state games, storing and analyzing their complete solutions efficiently, and serving them to GamesCrafters' user interfaces.}
            \resumeItem{Simple \textbf{multithreaded} implementations of solution set analyzer, solving algorithm, and DBMS modules.}
            \resumeItem{Working on supporting OpenMPI for solves on \textbf{High Performance Computing clusters}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Process} $|$ Task management application for iOS.}
          \resumeItemListStart
            \resumeItem{Allows for many-to-many \textbf{graph of task-subtask relationships}, as opposed to simple or nested lists.}
            \resumeItem{Served using \textbf{Firebase} Auth, Storage, and Firestore (although Neo4j is better suited for storing graphs of tasks).}
            \resumeItem{Features a \textbf{recursive UI} for intuitively traversing subtask items, built with Swift and SwiftUI.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Tools and Frameworks}{: Git, Mercurial, OpenMPI, OpenMP, SQL, Ent, React, SwiftUI.} \\
     \textbf{GPPLs}{: Rust, C/C++, Java, Swift, Python, JavaScript.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
